Symmetry-based constraints on the size of the dynamical Solar neighborhood

### 2019-04-09 paper/ms.tex
Minor changes throughout

\section{Azimuthal midplane variations at the Solar Circle: estimates from
FIRE} \label{sec:local_fire}
\subsection{Description of FIRE Simulation} \label{ssec:cosmozoom}
We briefly describe the cosmological-hydrodynamical zoom-in simulations used
in this work. Cosmological zoom-ins allow one to simulate a selected region at
high resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}, to which can be added
a hydrodynamical simulation of the baryonic component with recipes for star
formation and feedback. The FIRE collaboration has simulated a number of Milky
Way-mass galaxies using this technique as part of the {\em Latte} suite of
FIRE-2 simulations \citep{2016ApJ...827L..23W,2018MNRAS.481.4133G}. For this
work we focus on the three zoom-ins considered in \citet{2018arXiv180610564S},
which show broad agreement of many of their global properties with
observations of the Milky Way. The $\z=0$ snapshots\footnote{In this work, to
avoid confusion with the vertical height $z$, we refer to cosmological
redshift as $\z$.} of these three simulations, called \mi{}, \mf{}, and \mm{}
for shorthand, are publicly available alongside associated mock {\em Gaia} DR2
catalogues generated from them.\footnote{at \url{http://ananke.hub.yt}}

@@

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about
$40\,\pc$ ($3\text{-}4$ times the cold gas softening length;
\citealt{2019ApJ...871..145A}) and the thin stellar disk a scale height of
about 300 pc (30 times the stellar softening length;
\citealt{2008ApJ...673..864J}). We therefore expect that resolution effects
may still be affecting the scale heights of these components in the
simulations, especially the cold gas. Indeed, the stellar scale heights of the
simulated galaxies are equal to or larger than the MW's while the gas scale
heights are significantly larger (although the proper basis comparison is less
clear in the case of the gas; the quoted value for the Milky Way comes from
studies of high-mass star-forming regions). As noted above, the midplanes
defined by gas and stars can be tilted with respect to one another as well,
precluding extending the precision of the gas midplane definition to the
stellar component. In this work we specifically consider azimuthal variations
in the midplane \emph{as defined by the stellar mass density}, which will
subsequently be lower in the simulations than in the MW: within 200 pc of the
Sun the measured gas and stellar volume densities in the MW are roughly
comparable at $\sim .04\ \Msun\
\unit{pc}{-3}$, while in the simulations they are a factor of a few lower (see
Table 3 of \citealt{2018arXiv180610564S}). We thus expect that the degree of
midplane variation we find in the simulated systems is likely to be
\emph{less} than in the real MW, since on the smallest scales the simulations
are \emph{smoother} than the real Galaxy.

@@

\subsection{Local Midplane} \label{ssec:local_midplane}
Using the three simulations, we determine the local midplane that an observer
might measure if they were situated in each of these galaxies, as a function
of azimuth at the solar circle. Starting from the coordinate system described
in the previous section, which is approximately aligned so that the $z$
coordinate is perpendicular to the disk plane, we place our imaginary observer
at $z=0$ and a solar radius of $8.2\,\kpc$ and vary the azimuth between
$0<\phi<2\pi$\footnote{Our very long-lived observer also has warp-drive.}. At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define this median $z$ as the new midplane of the
cylinder, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$. This procedure assumes
perfect density estimation, and therefore perfect corrections for extinction,
within the cylinder defining the ``solar neighborhood.'' Imperfect extinction
correction is likely to increase the amplitude of the estimated fluctuations
in $z$. To account for the effect of particle noise, we bootstrap-resample
stars within a cylinder of stars with height $2\,\kpc$ and the same radius
$1000$ times and determine the $95^{\text{th}}$ minus $5^{\text{th}}$
percentile range. This bootstrap resampling is performed by first selecting
all stars within a height of $2\,\kpc$, resampling that selection, and then
repeating the $10$ iterations.

@@

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane our imaginary observer would determine as a function of azimuth for
each galaxy, using their local ``solar neighborhood'' (the cylinder defined
above). The $5\textup{--}95$ percentile range from the bootstrap procedure is
shown as the dashed-line error bars. The $90\%$ interquartile range for each
galaxy is $185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. In two of the
three cases the midplane therefore varies by more than $\pm 100\,\pc$
depending on the azimuth along the Solar circle; in the third (\mm{}, which
has the thinnest ``thin disk'' of stars, but the largest stellar mass) the
variation is more like $\pm 50\,\pc$.

@@

\subsection{LSR Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
, but performing a best-fit subtraction to correct for misalignment of the
original coordinate system (as in the previous section) is more involved.
Since the variation in the LSR is less pronounced than for the midplane, and
since the dominant effect is limited to $J_r$
(Figure~\ref{fig:many_orbit_wrong_ref}), we defer this calculation to future
work.

\section{Discussion} \label{sec:discussion}
We have used high-resolution cosmological simulations to illustrate that we
expect the ``local midplane'' defined by stellar density to vary with azimuth
by up to $\pm 100$ pc, as a natural consequence of the non-axisymmetry of the
Galactic disk at small scales. While this is not in itself surprising or new,
we also demonstrate that extending the coordinate system established by our
local midplane to a global axisymmetric coordinate system spanning the
entirety of the Galactic disk introduces systematic error in computations of
the actions under this symmetry assumption, when starting from the present-day
positions and velocities of stars as measured, for example, by \emph{Gaia}.
These systematic errors are most important for stars on thin-disk-like orbits,
where they can be large enough to yield actions representative of orbits in
the thick disk. This effect is entirely due to the extension of a local to a
global coordinate system, and is separate from real diffusion in stellar
integrals of motion caused by interactions with these same deviations from
axisymmetry, such as resonant perturbation by spiral arms or scattering from
molecular clouds.

@@

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.'' Since the
motivation may be different for defining the solar neighborhood in e.g.
studies of the chemical distribution of the Galaxy, we propose the phrase
``dynamical solar neighborhood.''

@@

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor{} horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047,
0.10\,\text{rad}$, with corresponding physical scales of $\lambda \sim 465,
610, 1290\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor{} horizontal line in Figure~\ref{fig:range_deltaphi}).
In fact, the range of midplane variation in \mi{} just barely saturates to
cause such an error in $J_z$, with the midplane variation in \mf{} and \mm{}
never reaching such a value. For stars on halo-like orbits, extending the
local coordinate system globally is not likely to cause serious problems,
since the midplane deviations are relatively small compared to those needed to
produce $\mathcal{O}(1)$ systematic errors in the actions (\halocolor{}
horizontal line in Figure \ref{fig:range_deltaphi}). However, we caution that
the tendency of these midplane deviations is to \emph{inflate} the value of
$J_z$ whenever the midplane deviation is $\gtrsim z_{\text{max}}$, scattering
them into the region of action space normally associated with different
stellar populations and possibly contributing to confusion there. This
inflation is extremely non-Gaussian (as the induced error is for all orbits,
e.g. Figure~\ref{fig:Jz_hist}), and is particularly troubling for the case of
thin disk stars, where the necessary midplane deviation is
$\sim50\textup{--}100\,\pc$.

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i - \bm{J}_c \in V_e$, where $V_e$ is centered on $J_c$ and has size
proportional to the intrinsic action-space dispersion of the disrupting
cluster. This dispersion can be estimated as \citep[Section~8.3.3
of][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m_c}{M}\right)^{1/3}\text{,}
\eeq
where $m_c$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit around the Galaxy, in this case assumed to be the mass inside
the Solar circle ($\sim 10^{11}\Msun$). Stars with actions within $V_e$ would
then be considered cluster members.

Two issues are immediately apparent with this approach. The first is that it
neglects the overall smooth distribution \emph{in action space} which will
contribute some stars to the selection by chance. For dissolving open clusters
in the thin disk, this background is not likely to be negligible, but we will
assume for the sake of argument that it can be modeled within the ``dynamical
solar neighborhood'' where it is safe to extend the local coordinate system.
Since the effect of extending the coordinate frame beyond this region is
generally to inflate the actions computed for thin-disk stars, using too large
a volume is likely to under-estimate the density of the smooth thin-disk-like
component in action space, while scattering more thin-disk stars onto
thick-disk-like orbits and over-estimating the density of the smooth
thick-disk-like component.

The second issue, which is related to the point of this paper, is that based
on the results in our previous sections computing $\bm{J}_i$ for a field star
and directly comparing it to  $\bm{J}_c$ will have significant systematic
error if the cluster and field star are far enough apart to have significantly
different local midplanes (see Figure \ref{fig:range_deltaphi}). Since our
criterion for cluster membership (distance in action space) scales with the
cluster mass, the region where the search will succeed varies with cluster
mass as well. To illustrate this effect, we assume a cluster mass $m_c$ and
estimate the expected action-space dispersion from
Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the midplane $z$ offset
necessary in order for the induced error in the vertical action to be the same
as the expected action-space dispersion. We perform this analysis for the
thin-disk-like and thick-disk-like orbits considered in
Section~\ref{ssec:quant}, assuming that the halo-like orbit is unlikely for
members of known open clusters (see Table~\ref{tab:real_clusters}). The result
for the allowable midplane offset for these two orbits in shown in Figure
\ref{fig:cluster_offset} as a function of cluster mass.

@@

We also compute $R_{\n}$ for each of the orbits of the real open clusters in
Table~\ref{tab:real_clusters}, using the midplane variations from
\mi{} as a conservative choice, since it has the largest degree of
midplane variation (Figure~\ref{fig:midplane}). We report the neighborhood
values for the mass of each cluster in the neighborhood column of
Table~\ref{tab:real_clusters}. Except for alphaPer, we find that the
neigbhorhood around each cluster is typically $\gtrsim 500\,\pc$. This
analysis assumes that the MW resembles \mi{}, which is not necessarily true.
However, this step of our analysis is meant to be more illustrative than
quantitative: this calculation should actually be performed using real
measurements of variations in the MW's stellar midplane. Such measurements
should be possible in the near future with Gaia, with quality distance
estimates the crucial limiting factor.

>>>>

\section{Azimuthal midplane variations at the Solar Circle: estimates from
simulation} \label{sec:local_fire}
\subsection{Description of FIRE Simulation} \label{ssec:cosmozoom}
We briefly describe the cosmological-hydrodynamical zoom-in simulations used
in this work. Cosmological zoom-ins allow one to simulate a selected region at
high resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}, to which can be added
a hydrodynamical simulation of the baryonic component with recipes for star
formation and feedback. The FIRE collaboration has simulated a number of Milky
Way-mass galaxies using this technique as part of the {\em Latte} suite of
FIRE-2 simulations \citep{2016ApJ...827L..23W,2018MNRAS.481.4133G}. For this
work we focus on the three zoom-ins considered in \citet{2018arXiv180610564S},
which show broad agreement of many of their global properties with
observations of the Milky Way. The $\z=0$ snapshots\footnote{In this work, to
avoid confusion with the vertical height $z$, we refer to cosmological
redshift as $\z$.} of these three simulations, called \mi{}, \mf{}, and \mm{}
for shorthand, are publicly available alongside associated mock {\em Gaia} DR2
catalogues generated from them.\footnote{\url{http://ananke.hub.yt}}

@@

The softening lengths used in the simulations can affect the ability to
resolve the very thinnest planar structures, which in turn can affect how much
the density-based midplane varies as a function of azimuth. The Milky Way's
dense, star-forming gas disk is thought to have a scale height of about
$40\,\pc$ ($3\text{-}4$ times the cold gas softening length;
\citealt{2019ApJ...871..145A}) and the thin stellar disk a scale height of
about 300 pc (30 times the stellar softening length;
\citealt{2008ApJ...673..864J}). We therefore expect that resolution effects
may still be affecting the scale heights of these components in the
simulations, especially the cold gas. Indeed, the stellar scale heights of the
simulated galaxies are equal to or larger than the MW's while the gas scale
heights are significantly larger (although the proper basis comparison is less
clear in the case of the gas; the quoted value for the Milky Way comes from
studies of high-mass star-forming regions). As noted above, the midplanes
defined by gas and stars can be tilted with respect to one another as well,
precluding extending the precision of the gas midplane definition to the
stellar component. In this work we specifically consider azimuthal variations
in the midplane \emph{as defined by the stellar mass density}, which will
subsequently be lower in the simulations than in the MW: within 200 pc of the
Sun the measured gas and stellar volume densities in the MW are roughly
comparable at $\sim 0.04\ \Msun\
\unit{pc}{-3}$, while in the simulations they are a factor of a few lower (see
Table 3 of \citealt{2018arXiv180610564S}). We thus expect that the degree of
midplane variation we find in the simulated systems is likely to be
\emph{less} than in the real MW, since on the smallest scales the simulations
are \emph{smoother} than the real Galaxy.

@@

\subsection{Local Midplane} \label{ssec:local_midplane}
Using the three simulations, we determine the local midplane that an observer
might measure if they were situated in each of these galaxies as a function
of azimuth at the solar circle. Starting from the coordinate system described
in the previous section, which is approximately aligned so that the $z$-coordinate is perpendicular to the disk plane, we place our imaginary observer
at $z=0$ and a solar radius of $8.2\,\kpc$ and vary the azimuth between
$0<\phi<2\pi$\footnote{Our very long-lived observer also has warp drive.}. At
each value of $\phi$ we then compute the median $z$ for stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk. We then re-define this median $z$ as the new midplane of the
cylinder, re-select stars, and iterate until the median $z$ value converges.
We find that only $10$ iterations of this procedure are necessary for
convergence. The resulting median $z$ is taken to be what our observer would
measure as the local Galactic midplane at each $\phi$. This procedure assumes
perfect density estimation, and therefore perfect corrections for extinction,
within the cylinder defining the ``solar neighborhood.'' Imperfect extinction
correction is likely to increase the amplitude of the estimated fluctuations
in $z$. To account for the effect of particle noise, we bootstrap-resample
stars within a cylinder of stars with height $2\,\kpc$ and the same radius
$1000$ times and determine the $1\,\sigma$ error bars. This bootstrap resampling is performed by first selecting
all stars within a height of $2\,\kpc$, resampling that selection, and then
repeating the $10$ iterations.

@@

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane our imaginary observer would determine as a function of azimuth for
each galaxy, using their local ``solar neighborhood'' (the cylinder defined
above). The $5\textup{--}95$ percentile range from the bootstrap procedure is
shown as the dashed-line error bars. The middle $90\%$ of midplane values across the Solar circle spans $185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. In two of the
three cases the midplane therefore varies by more than $\pm 100\,\pc$
depending on the azimuth along the Solar circle; in the third (\mm{}, which
has the thinnest ``thin disk'' of stars, but the largest stellar mass) the
variation is more like $\pm 50\,\pc$.

@@

\subsection{LSR Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
the components of the LSR as a function of azimuth, but performing a best-fit
subtraction to correct for misalignment of the original coordinate system (as
in the previous section) is more involved. Since we find that the variation in
the LSR is less pronounced than for the midplane, and since the dominant
effect is limited to $J_r$ (Figure~\ref{fig:many_orbit_wrong_ref}), we defer
this calculation to future work.

\section{Discussion} \label{sec:discussion}
We have used high-resolution cosmological simulations to illustrate that we
expect the ``local midplane'' defined by stellar density to vary with azimuth
by up to $\pm 100$ pc, as a natural consequence of the non-axisymmetry of the
Galactic disk at small scales. While this is not in itself surprising or new,
we also demonstrate that extending the coordinate system established by our
local midplane to a global axisymmetric coordinate system spanning the
entirety of the Galactic disk introduces systematic error in computations of
the actions under this symmetry assumption, when starting from the present-day
positions and velocities of stars as measured by, e.g., \emph{Gaia}.
These systematic errors are most important for stars on thin disk-like orbits,
where they can be large enough to yield actions representative of orbits in
the thick disk. This effect is entirely due to the extension of a local to a
global coordinate system, and is separate from real diffusion in stellar
integrals of motion caused by interactions with these same deviations from
axisymmetry, such as resonant perturbation by spiral arms or scattering from
molecular clouds.

@@

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.'' Since the
motivation may be different for defining the solar neighborhood in, e.g.,
studies of the chemical distribution of the Galaxy, we propose the phrase
``dynamical solar neighborhood.''

@@

From Figure~\ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor{} horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047,
0.10\,\text{rad}$, with corresponding physical scales of $\lambda \sim 465,
610, 1290\,\pc$ for \mi{}, \mf{}, and \mm{}, respectively. These can be
considered estimates of the range of validity for an extension of the locally
determined axisymmetric coordinate system, at least when it comes to the study
of stars on quasi-circular orbits.

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor{} horizontal line in Figure~\ref{fig:range_deltaphi}).
In fact, the range of midplane variation in \mi{} just barely saturates to
cause such an error in $J_z$, with the midplane variation in \mf{} and \mm{}
never reaching such a value. For stars on halo-like orbits, extending the
local coordinate system globally is not likely to cause serious problems,
since the midplane deviations are relatively small compared to those needed to
produce $\mathcal{O}(1)$ systematic errors in the actions (\halocolor{}
horizontal line in Figure \ref{fig:range_deltaphi}). However, we caution that
the tendency of these midplane deviations is to \emph{inflate} the value of
$J_z$ whenever the midplane deviation is $\gtrsim z_{\text{max}}$, scattering
them into the region of action space normally associated with different
stellar populations and possibly contributing to confusion there (see Figure~\ref{fig:Jz_hist} and discussion therein). This
inflation is extremely non-Gaussian (as the induced error is for all orbits,
e.g. Figure~\ref{fig:Jz_hist}), and is particularly troubling for the case of
thin disk stars, where the necessary midplane deviation is
$\sim50\textup{--}100\,\pc$.

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i \in V_e$, where $V_e$ is a volume centered on $\bm{J}_c$ and has size
comparable to the intrinsic action-space dispersion of the disrupting
cluster. This dispersion can be estimated as \citep[Section~8.3.3
of][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m_c}{M}\right)^{1/3}\text{,}
\eeq
where $m_c$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit around the Galaxy, in this case assumed to be the mass inside
the Solar circle ($\sim 10^{11}\Msun$). Stars with actions within $V_e$ would
then be considered cluster members.

Two issues are immediately apparent with this approach. The first is that it
neglects the overall smooth distribution \emph{in action space} which will
contribute some stars to the selection by chance. For dissolving open clusters
in the thin disk, this background is likely to be significant, but we will
assume for the sake of argument that these foreground stars can be modeled within the ``dynamical
solar neighborhood'' where it is safe to extend the local coordinate system.
Since the effect of extending the coordinate frame beyond this region is
generally to inflate the actions computed for thin-disk stars, using too large
a volume is likely to under-estimate the density of the smooth thin-disk-like
component in action space, while scattering more thin-disk stars onto
thick-disk-like orbits and over-estimating the density of the smooth
thick-disk-like component.

The second issue, which is related to the point of this paper, is that based
on the results in our previous sections computing $\bm{J}_i$ for a field star
and directly comparing it to  $\bm{J}_c$ will have significant systematic
error if the cluster and field star are far enough apart to have significantly
different local midplanes (see Figure \ref{fig:range_deltaphi}). Since our
criterion for cluster membership (distance in action space) scales with the
cluster mass, the region where the search will succeed varies with cluster
mass as well. To illustrate this effect, we assume a cluster mass $m_c$ and
estimate the expected action-space dispersion from
Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the midplane offset
necessary in order for the induced error in the vertical action to be the same
as the expected action-space dispersion. We perform this analysis for the
thin-disk-like and thick-disk-like orbits considered in
Section~\ref{ssec:quant}, assuming that the halo-like orbit is unlikely for
members of known open clusters (see Table~\ref{tab:real_clusters}). The result
for the allowable midplane offset for these two orbits in shown in Figure~\ref{fig:cluster_offset} as a function of cluster mass.

@@

We also compute $R_{\n}$ for each of the orbits of the real open clusters in
Table~\ref{tab:real_clusters}, using the midplane variations from
\mi{} as a conservative choice, since it has the largest degree of
midplane variation (Figure~\ref{fig:midplane}). We report the neighborhood
values for the mass of each cluster in the neighborhood column of
Table~\ref{tab:real_clusters}. Except for alphaPer, we find that the
neigbhorhood around each cluster is typically $\gtrsim 500\,\pc$. This
analysis assumes that the MW resembles \mi{}, which is not necessarily true.
However, this step of our analysis is meant to be more illustrative than
quantitative: this calculation should actually be performed using real
measurements of variations in the MW's stellar midplane. Such measurements
should be possible in the near future with {\em Gaia}, with quality distance
estimates the crucial limiting factor.
